---
title: "MIS40970 Assignment 1 Orange Juice Sales"
output:
  html_notebook: default
  pdf_document:
    number_sections: yes
    toc: yes
---
##1. Load the oj.csv data into R.
```{r}
options(warn = 1)
oj <- read.csv(file="E:\Smurfit\Semester 2\DM\R\Data-Mining",head=TRUE,sep=",")
summary(oj)
```
##2. How many records and how many attributes are in the orange juice dataset?


```{r}
dim(oj)
names(oj)
```
##3. What is the mean, standard deviation and range of the price of orange juice?
```{r}
mean(oj$price)
sd(oj$price)
range(oj$price)
```

##4. What is the median of the 'log of number of units sold' (logmove)?
```{r}
median(oj$logmove)
```

##5. What are the names of the 3 orange juice brands? (Hint: brand is of type factor, and a factor is comprised of a number of ...<insert function name here!...)
```{r}
unique(oj$brand)
juicebrand<- factor(oj$brand)
table(juicebrand)
```
##6. Create a histogram of prices for each brand of orange juice.
```{r}
hist(oj$price[oj$brand=='tropicana'],main=" Price of Tropicana Orange Juice",xlab="Price",breaks =50, col = 'brown')
hist(oj$price[oj$brand=='minute.maid'],main=" Price of Mindute Maid Orange Juice",xlab="Price",breaks =50,col='Red')
hist(oj$price[oj$brand=='dominicks'],main=" Price of Dominicks Orange Juice",xlab="Price",breaks =50, col = 'blue')

"Alternative Method Using ggplot2"
library(ggplot2)
ggplot(oj, aes(x= oj$price, fill = brand)) + geom_histogram(binwidth=1,position = "dodge")+ ylab("Count") +
  xlab("Orange Juice Price") +
  ggtitle("Prices of Orange Juice and Count of Each Type")
```

##7. Generate a boxplot, which includes a separate plot for the prices of each brand (Hint: the boxplot should look something like the example below)
```{r}
boxplot(oj$price~oj$brand, data=oj, notch=TRUE, 
  col=(c("gold","darkgreen")),main="Boxplot of Prices for each Orange Juince brand", xlab="Price and Brand name")
```
##8. What does the boxplot tell us about the relative prices of each brand?
(Hint: answer this one by interpreting what you observe in the boxplot,
i.e., no coding required!).

##9. Generate a scatterplot of the logmove compared to price, and color
the points according to their brand (e.g., "red" for brand 1, "green"
for brand 2 etc).
```{r}
library(scatterplot3d)
attach(oj)
pairs(~logmove+price, pch=21,main="Scatter plot of Log of the number of units Sold vs Price of Orange Juice",bg= c("red", "blue", "yellow")[unclass(brand)])

plot(logmove,price, xlab="Units Sold",ylab="Price",pch=21,col=topo.colors(3)[unclass(brand)])
legend("bottomleft", inset=0.01, title="Brands",c("Tropicana","Minute Maid","Dominicks"), fill=topo.colors(3), horiz=FALSE)
```
```{r}
library(plotly)
Sys.setenv("plotly_username"="deepak91g")
Sys.setenv("plotly_api_key"="Gb3tMDu2UzMuGdXsMB9n")

p <- plot_ly(data = oj, x = ~logmove, y = ~price, color = ~brand, colors = "Set1")

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="colorbrewer")
chart_link
```

##10. Based on what you observe in the scatterplot, what can we say about
the price of each brand of chilled orange juice and the volume of sales?
##11. Calculate the mean price of orange juice sold each week, and create a
line plot of this timeseries. (Hint: use tapply(), and an example plot
is provided below.)

Note: Using tapply() method here

```{r}
xnames <- tapply(oj$price,oj$week,FUN=mean,na.rm=TRUE)
plot(tapply(oj$price,oj$week,FUN=mean,na.rm=TRUE),xaxt="n",pch=16,type="l",col="green",xlab = "Week",ylab="meanweeklyprice")
```
NOTE: Answer to question 11, using aggreagate method
```{r}
meanweeklyprice <- aggregate(oj[ ,6], list(oj$week), mean)
plot(meanweeklyprice$Group.1,meanweeklyprice$x,type="l",col="green",xlab = "Week",ylab="meanweeklyprice")

```
##12. Extract the mean weekly price of orange juice sold each week according
to each brand (Hint: use tapply() with a list for the INDEX)
```{r}
#Solution :1 using aggregate()
mean_weekly_brand_price <- aggregate(oj[ ,6], list(Brand=oj$brand,Week=oj$week), mean)
mean_weekly_brand_price
#Solution :2 using tapply()
weekly_brand_price<-tapply(oj$price,list(Week=oj$week,oj$brand),FUN=mean,na.rm=TRUE)
weekly_brand_price
```

##13. Create a plot which compares the mean weekly price of orange juice
for all brands versus each individual brand.
```{r}
weekly_brand_price<-tapply(oj$price,list(Week=oj$week,oj$brand),FUN=mean,na.rm=TRUE)
allbrand <- tapply(oj$price,list(Week=oj$week),FUN=mean,na.rm=TRUE)
df <- cbind(allbrand,weekly_brand_price)
write.table(df, file = 'q13.csv',sep = ",",row.names = T)
library(readr)
q13 <- read_csv("E:/Smurfit/Semester 2/DM/R/Data-Mining/q13.csv", 
    col_names = FALSE, skip = 1)
ggplot(q13, aes(q13$X1)) + 
  geom_line(aes(y = q13$X2, colour = "All Brand")) + 
  geom_line(aes(y = q13$X3, colour = "Dominicks")) + 
  geom_line(aes(y = q13$X4, colour = "Minute Maid")) + 
  geom_line(aes(y = q13$X5, colour = "Tropicana")) + xlab("Week") +ylab("Price")+
  ggtitle("Weekly price of Orange Juice for All Brands vs Individual Brand")
```


##14.When there is an advertising campaign for orange juice does it impact on the number of units sold? (Hint: use factor() to ensure feat is a factor! and use tapply as per the last question).
```{r}
adcap <- factor(oj$feat)
tapply(oj$logmove,adcap,FUN=mean,na.rm=TRUE)
```
## 15. Can you create a line plot of the mean weekly units sold without a promotion overlayed with the mean weekly units sold with a promotion? What is interesting about this plot?

Answer: With a promotion more number of units sold as compared to campaign without a promotion 
```{r}
options(warn = -1)
unitsold<-tapply(logmove,list(oj$week),FUN=mean,na.rm=TRUE)
head(unitsold)
sold <- tapply(oj$logmove,list(Week=oj$week,oj$feat),FUN=mean,na.rm=TRUE)
df <- cbind(sold)
write.table(df, file = 'q15.csv',sep = ",",row.names = T)
library(readr)
q15 <- read_csv("E:/Smurfit/Semester 2/DM/R/Data-Mining/q15.csv", 
    col_names = FALSE, skip = 1)
ggplot(q15, aes(q13$X1,xlab="Week")) + 
  geom_line(aes(y = q13$X2, colour = "With promotion")) + 
  geom_line(aes(y = q13$X3, colour = "Without promotion"))+ xlab("Week") +ylab("Units Sold")+
  ggtitle("Mean weekly units sold with a promotion vs without promotion") 
```
##16.Consider the demographic and competitive variables1. Using descriptive analytics are there patterns you can observe that might suggest the potential for proling individual stores or customers, which might then be used for marketing purposes?
```{r}

```








